Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/related_work.tex
intro and rel work

In this work we extend supervised latent Dirichlet allocation (sLDA) \cite{BleiMcAuliffe2008} to take advantage of hierarchical supervision.  sLDA is latent Dirichlet allocation (LDA) \cite{Blei2003} augmented with per document ``supervision'';  often taking the form of a single numerical or categorical label. More generally this supervision is just extra per-document data;  for instance its quality or relevance (e.g.~online review scores), marks given to written work (e.g.~essay grades), or the number of times a web page is linked.  These labels are usually generatively modeled as a conditional draw from some distribution that depends on each document-specific topic mixture.  It has been demonstrated that the signal provided by such supervision can result in better, task-specific document models and can also lead to good label prediction for out-of-sample data \cite{BleiMcAuliffe2008}.  It also has been demonstrated that sLDA has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression~\cite{BleiMcAuliffe2008}.  sLDA can be applied to data of the type we consider in this paper; however, doing so requires ignoring the hierarchical dependencies amongst the labels.  In Section~\ref{sec:experiments} we constrast HSLDA with sLDA applied in this way.

@@

In other work, researchers have classified documents into a hierarchy (a closely related task) with naive Bayes classifiers
and support vector machines. Most of this work has been demonstrated on relatively
small datasets, small label spaces, and has focused on single label classification without
a model of documents such as LDA\citep{mccallum99building,Dumais2000HCW,Kollerilprints291,Chakrabarti1998SFS}.

>>>>

In this work we extend supervised latent Dirichlet allocation (sLDA)
\cite{BleiMcAuliffe2008} to take advantage of hierarchical supervision. sLDA
is latent Dirichlet allocation (LDA) \cite{Blei2003} augmented with per
document ``supervision,'' often taking the form of a single numerical or
categorical label. It has been demonstrated that the signal provided by such
supervision can result in better, task-specific document models and can also
lead to good label prediction for out-of-sample data \cite{BleiMcAuliffe2008}.
It also has been demonstrated that sLDA has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least squares
regression~\cite{BleiMcAuliffe2008}. sLDA can be applied to data of the type
we consider in this paper; however, doing so requires ignoring the hierarchical
dependencies amongst the labels. In Section~\ref{sec:experiments} we constrast
HSLDA with sLDA applied in this way.

@@

In other work, researchers have classified documents into a hierarchy (a closely related task) with naive Bayes classifiers
and support vector machines. Most of this work has been demonstrated on relatively
small datasets, small label spaces, and has focused on single label classification without
a model of documents such as LDA~\citep{mccallum99building,Dumais2000HCW,Kollerilprints291,Chakrabarti1998SFS}.
